Quality Definitions of Qualities

### 2022-02-25 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Udpates to SOP for MI up to Section 3.2 (List of Representative Software)
Minor notes added to qdef paper
Addition of a reference on sustainability to use for the quality definitions paper
Minor typo corrections

@@

It would be worthwhile to look for some additional definitions.

@@

\wss{Reproducibility literature review is given in \citet{FeinbergEtAl2020}.
Includes examples where replicability was found to be lacking.  Has a good
litereature review in Section 2.}

@@

>>>>

\wss{Add definitions from ``Continuous quality control of long lived software systems''}

@@

It would be worthwhile to look for some additional definitions.  Definitions are
found here: \href{https://www.ncbi.nlm.nih.gov/books/NBK547546/}{Understsanding
Reproducibility and Replicability}

@@

\wss{Reproducibility literature review is given in \citet{FeinbergEtAl2020}.
Includes examples where replicability was found to be lacking.  Has a good
literature review in Section 2.}

@@

Additional references on sustainability can be found in \citet{FerrariEtAl2021}.
